### 2023-01-18 files/Chapter3/femconvergence.tex
Chapter 3 end 95%

\newtheorem{Prop_2}[Prop_1]{Proposition}
\begin{Prop_2}
	$\lambda^{h}_{m} \leq \max R(Pu) \ \text{ for } u \in B_{m}$\\
\end{Prop_2}
\begin{proof}
	Since $\dim S_{m} = m$, following from the minmax principle
	\begin{equation*}
		\lambda_m^h \leq \max R(v) \ \text{ for } v \in S_m.
	\end{equation*}

@@

\newtheorem{Lem_1}{Lemma}
\begin{Lem_1}
	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}$
\end{Lem_1}
\begin{proof}
	Consider the linearity of the bilinear form $b$, and fact that any $u \in E_m$ can be expressed as a linear combination $u = \sum_{i=1}^{m} c_{i}u_{i}$. Then
	\begin{eqnarray*}
	b(u,u) &=& b\left(\sum_{i=1}^{m} c_{i}u_{i},\sum_{j=1}^{m} c_{j}u_{j}\right),\\
			&=& \sum_{i=1}^{m} c_{i}\sum_{j=1}^{m} c_{j} b(u_{i},u_{j}).
	\end{eqnarray*}

@@

	$b(u,u) = \sum_{i=1}^{m} c_{i}^{2} \lambda_{i} \leq \lambda_{m}\sum_{i=1}^{m} c_{i}^{2} =\lambda_{m} ||u||^{2}$ for all $u \in E_{m}$.\\
	And since $B_{m} \subset E_{m}$, we have $b(Pu,Pu) \leq \lambda_{m}$ for all $u\in B_{m}$\\

	So now from the definition of $\mu_{m}^{h}$ and the Rayleigh quotient, we have
	\begin{eqnarray*}
		R(Pu) &=& \frac{b(Pu,Pu)}{(Pu,Pu)}\\
			&=& \frac{b(Pu,Pu)}{||Pu||^{2}}\\
			&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}
	\end{eqnarray*}
	This together with Proposition 7.1 gives
	\begin{eqnarray*}
		\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}
	\end{eqnarray*}
\end{proof}
\begin{comment}
\textbf{Proof:} Let $Y = \sum_{i=1}^{m} c_{i}u_{i}$.
\begin{eqnarray*}
b(u,u) &=& b\left(\sum_{i=1}^{m} c_{i}u_{i},\sum_{j=1}^{m} c_{j}u_{j}\right)\\
		&=& \sum_{i=1}^{m} c_{i}\sum_{j=1}^{m} c_{j} b(u_{i},u_{j})
\end{eqnarray*}
\textbf{RTP:} $\left\{u_{1},u_{2},...,u_{m}\right\}$ is orthonormal.\\
Pick any $i,j \in \mathbb{N}$ such that $i,j \leq m$. Let arbitrary $v_{i},v_{j} \in V$ be arbitrary, then
\begin{eqnarray*}
	b(u_{i},u_{i}) &=& \lambda_{i}( u_{i},u_{i})\\
	b(u_{j},u_{j}) &=& \lambda_{j}( u_{j},u_{j})
\end{eqnarray*}
Now we pick $u_{i} = u_{j}$ and $u_{j} = u_{i}$. Then
\begin{eqnarray*}
	b(u_{i},u_{j}) &=& \lambda_{i}( u_{i},u_{j})\\
	b(u_{j},u_{i}) &=& \lambda_{j}( u_{j},u_{i})
\end{eqnarray*}
Then using the symmetry of $b(\cdot,\cdot)$ and $( \cdot, \cdot )$, and subtracting, we get
\begin{eqnarray*}
 0 &=& (\lambda_{i} - \lambda_{j})( u_{i}, u_{j} )
\end{eqnarray*}
So if $i \neq j$, $\lambda_{i} \neq \lambda_{j}$. Thus we must have that $u_{i}$ and $u_{j}$ are orthogonal. And since by the way $u_{i}$ is defined, $||u_{i}|| = 1$. So thus $\left\{u_{1},u_{2},...,u_{m}\right\}$ is orthonormal.\\

So then $b(u,u) = \sum_{i=1}^{m} c_{i}^{2} \lambda_{i} \leq \lambda_{m}\sum_{i=1}^{m} c_{i}^{2} =\lambda_{m} ||u||^{2}$ for all $u \in E_{m}$.\\
And since $B_{m} \subset E_{m}$, we have $b(Pu,Pu) \leq \lambda_{m}$ for all $u\in B_{m}$\\

So now from the definition of $\mu_{m}^{h}$ and the Rayleigh quotient, we have
\begin{eqnarray*}
	R(Pu) &=& \frac{b(Pu,Pu)}{(Pu,Pu)}\\
		&=& \frac{b(Pu,Pu)}{||Pu||^{2}}\\
		&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}
\end{eqnarray*}
This together with Proposition 7.1 gives
\begin{eqnarray*}
	\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}
\end{eqnarray*}\qed
\end{comment}

Now since $\lambda_{i}^{h} \geq \lambda_{i}$ and by Lemma 7.1, we must then have that $0 < \mu_{m}^{h} \leq 1$. Now define the error estimate as
\begin{eqnarray*}
\sigma_{m}^{h} = 1 - \mu_{m}^{h}
\end{eqnarray*}

%\newpage

\textbf{Corollary 7.1:} $0 \leq \sigma_{m}^{h} < 1$ and $\lambda_{m}^{h} - \lambda_{m} \leq \lambda_{m}^{h}\sigma_{m}^{h}$\\

\begin{comment}
\textbf{Proof:}
\begin{eqnarray*}
\lambda_{m}^{h} & \leq & \frac{\lambda_{m}}{\mu_{m}^{h}} \ \ \textrm { (by Lemma 7.1)} \\
\lambda_{m}^{h}\mu_{m}^{h}& \leq & \lambda_{m} \\
-\lambda_{m}& \leq & -\lambda_{m}^{h}\mu_{m}^{h} \\
\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h} -\lambda_{m}^{h}\mu_{m}^{h}\\
\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h}\sigma_{m}^{h}
\end{eqnarray*}\qed

So from this Corollary 7.1, we see that to prove that our approximate eigenvalues converge to the exact eigenvalues. The only thing then left to prove is  that $\sigma_{m}^{h} \rightarrow 0$ as $h \rightarrow 0$.\\
\\

\textbf{Proposition 7.1} $\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}$\\

\textbf{Proof:}  Let $u \in B_{m}$. Then
\begin{eqnarray*}
||u - Pu||^{2} &=& ( u - Pu, u - Pu ) \\
				&=& ( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ) \\
				&=& 2( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ) - ( u, u )\\
				&=& 2( u, u - Pu ) + ( Pu, Pu ) - ( u, u )\\
( u, u ) - ( Pu, Pu )  & = & 2( u, u - Pu ) - ||u - Pu||^{2}	
\end{eqnarray*}
Now since $u \in B_{m}$, $<u,u> = 1$. So we have
\begin{eqnarray*}
1 - ||Pu||^{2}  & = & 2( u, u - Pu ) - ||u - Pu||^{2}	
\end{eqnarray*}
Now the right hand side, $1 - ||Pu||^{2} \leq 1 - \mu_{m}^{h} = \sigma_{m}^{h}$ for all $u \in B_{m}$. So then we must have that
\begin{eqnarray*}
\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}
\end{eqnarray*}\qed
\end{comment}

Next we introduce some new notation to ease the writing. For any $u \in E_{m}$, let $u^{*} = \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}$ where $u = \sum_{i=1}^{m} c_{i}u_{i}$.\\

%\newpage

\textbf{Proposition 7.3:} For any $u \in E_{m}$
\begin{eqnarray*}
( u, u - Pu ) = b(u^{*} - Pu^{*}, u -Pu)
\end{eqnarray*}

\begin{comment}
\textbf{Proof:} For any $i = 1,2,...,m$, we have that
\begin{eqnarray*}
\lambda_{i}( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu)\\
									&=& b(u_{i}, u-Pu) - b(u-Pu,Pu_{i}) \ \textrm{ (by definition of Rayleigh-Ritz Projection)}\\
									&=&  b(u_{i}, u-Pu) - b(Pu_{i},u-Pu)\\
									&=&  b(u_{i}-Pu_{i}, u-Pu)
\end{eqnarray*}
So multiplying by $c_{i}\lambda_{i}^{-1}$ and summation over i gives:
\begin{eqnarray*}
\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu)\\
									&=& b(\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}Pu_{i}, u-Pu)\\
									&=& b(u^{*}-Pu^{*}, u-Pu)
\end{eqnarray*}
So $( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.\qed\\
\end{comment}

\textbf{Lemma 7.2:} $\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$\\

\begin{comment}
\textbf{Proof:} From Proposition 7.1, we have
\begin{eqnarray*}
\sigma_{m}^{h} &=& \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \} \\
				&\leq & \max\left\{ 2( u,u-Pu ) \ | \ u \in B_{m} \right \}
\end{eqnarray*} since $||u-Pu||^{2} \geq 0$.\\
\end{comment}

Using Proposition 7.3
\begin{eqnarray*}
\sigma_{m}^{h} &\leq & \max\left\{ 2b(u^{*} - Pu^{*}, u -Pu) \ | \ u \in B_{m} \right \}			
\end{eqnarray*}
Now
\begin{eqnarray*}
b(u^{*} - Pu^{*}, u -Pu) & \leq & ||u^{*} - Pu^{*}||||u -Pu|| \ \textrm{ (Schwartz inequality)} \\
\end{eqnarray*}
Thus  $\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$. \qed

%\newpage

\textbf{Proposition 7.3:} For any $\epsilon > 0$, there exists a $\delta >0$ such that for $h<\delta$,
\begin{eqnarray*}
||u^{*} - Pu^{*}|| < \epsilon \ \textrm{ for each } u \in B_{m}\\
||u - Pu|| < \epsilon \ \textrm{ for each } u \in B_{m}
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}
Suppose we have a set of basis functions $\Phi \subset S^{h}$ such that each element in $\Phi$ has order k, i.e. for each $v \in \Phi$, $v^{(k)} = 0$. Now from the definition of the Rayleigh-Ritz Projection, we have that $Pu$ is the closest element in $S^{h}$ to $u$. In particular, $||u-Pu||\leq ||u-\Pi u||$, where $\Pi u$ is the interpolant of $u$ into $S^{h}$.\\

Now from, we use the Approximation Theorem, so that we have
\begin{eqnarray*}
||u - \Pi u|| \leq Ch^{k}||u^{(k)}||
\end{eqnarray*}
So for any $\epsilon > 0$, we can find a $\delta$ such that if $h<\delta$ then
\begin{eqnarray*}
||u - Pu|| \leq ||u - \Pi u|| \leq \epsilon
\end{eqnarray*}
A similar argument for $||u^{*} - Pu^{*}||$ proves the theorem.
\qed
\\
\end{comment}

\textbf{Lemma 7.4:} For any $\epsilon >0$ there exists a $\delta > 0$ such that
\begin{eqnarray*}
\sigma_{m}^{h} < \epsilon \ \textrm{ if } \ h < \delta
\end{eqnarray*}

\begin{comment}
\textbf{Proof:} For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
\begin{eqnarray*}
||u-Pu|| < \epsilon \ \textrm{ for each } \ u \in B_{m}
\end{eqnarray*}
This, together with Lemma 7.2 and Proposition 7.4 gives the result.\qed\\
\end{comment}

\textbf{Lemma 7.5:} There exists a $\delta > 0$ such that for $h < \delta$
\begin{eqnarray*}
\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}
Using Lemma 7.4, choose $\delta$ such that $\sigma_{m}^{h} < \frac{1}{2}$. Then by Lemma 7.1 gives that $\lambda_{m}^{h} < 2\lambda_{m}$. So we have that
$\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
\qed
\end{comment}

\subsection{Convergence of the eigenfunctions}
So from Lemma 7.4, it is that if $h \rightarrow 0$, we will get convergence in the eigenvalues. The next step is now to use this, to show convergence in the eigenvectors.\\

\textbf{Lemma 7.6:}
\begin{eqnarray*}
b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& \lambda_{m}( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h} ) + \lambda_{m}^{h} - \lambda_{m}
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}
\begin{eqnarray*}
b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& b(u_{m},u_{m}) - 2b(u_{m},u^{h}_{m}) + b(u^{h}_{m},u^{h}_{m}) \\
								&=& \lambda_{m} ( u_{m}, u_{m} ) - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h}( u_{m}^{h},u_{m}^{h} )\\
								&=&  \lambda_{m} - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} \\
								&=& 2\lambda_{m} - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} - \lambda_{m}\\
								&=& \lambda_{m}( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) + \lambda_{m}^{h} - \lambda_{m}
\end{eqnarray*}
\qed
\end{comment}

We have already shown that $\lambda_{m}^{h} \rightarrow \lambda_{m}$. So it remains only to show that $( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$

Now we have the possibility that an eigenvalue, say $\lambda_{m}$ has multiplicity $r>1$. This implies that there are at least two eigenfunctions that correspond to this eigenvalue.\\

The Euler-Bernoulli beam however, only has a repeated eigenvalue if we consider the free-free boundary conditions. Then the beam would have a zero eigenvalue with multiplicity more than 1. Our model, however, does not have repeated eigenvalues. So we may assume that all the eigenvalues has multiplicity $r=1$.\\

\textbf{Lemma 7.7:} For all m and j
\begin{eqnarray*}
(\lambda_{j}^{h} - \lambda_{m}) ( Pu_{m}, u_{j}^{h}) = \lambda_{m} ( u_{m}-Pu_{m},u_{j}^{h} )
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}
Since the term $\lambda_{m}( Pu,u^{h}_{j})$ appears on both sides of the equation, it is only required to show that
\begin{eqnarray*}
\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& \lambda_{m} ( u, u_{j}^{h} )
\end{eqnarray*}
Now
\begin{eqnarray*}
\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& b(Pu,u_{j}^{h})\\
\lambda_{m} ( u, u_{j}^{h} ) &=& b(u,u_{j}^{h})
\end{eqnarray*} Since $u$ and $u_{j}^{h}$ are both eigenfunctions.\\

Then equality follows from the definitions of the projection P.
\qed
\end{comment}

The set $\left\{u_{1}^{h},u_{2}^{h},...,u_{N}^{h}\right\}$ then forms an orthonormal basis for $S^{h}$. So we can then write a projection $Pu_{m}$ as:
\begin{eqnarray}
Pu_{m} &=& \sum_{j=1}^{N} ( P u_{m} ,u_{j}^{h}) u_{j}^{h} \label{CV1}
\end{eqnarray}

From Lemma 7.8, we see that $( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$. So then (\ref{CV1}) tells us then that $Pu_{m}$ is close to $u_{m}^{h}$. This will allow us to estimate $Pu_{m} - u_{m}^{h}$.\\

>>>>

\newtheorem{Prop_2}[Prop_1]{Proposition} \label{Prop_2}
\begin{Prop_2}
	$\lambda^{h}_{m} \leq \max R(Pu) \ \text{ for } u \in B_{m}$\\
\end{Prop_2}
\begin{proof}
	Since $\dim S_{m} = m$, following from the minmax principle
	\begin{equation*}
		\lambda_m^h \leq \max R(v) \ \text{ for } v \in S_m.
	\end{equation*}

@@

\newtheorem{Lem_1}{Lemma} \label{Lem_1}
\begin{Lem_1}
	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{u_{m}^{h}}$
\end{Lem_1}
\begin{proof}
	Consider the linearity of the bilinear form $b$, and fact that any $u \in E_m$ can be expressed as a linear combination $u = \sum_{i=1}^{m} c_{i}u_{i}$. Then
	\begin{eqnarray*}
	b(u,u) &=& b\left(\sum_{i=1}^{m} c_{i}u_{i},\sum_{j=1}^{m} c_{j}u_{j}\right),\\
			&=& \sum_{i=1}^{m} c_{i}\sum_{j=1}^{m} c_{j} b(u_{i},u_{j}).
	\end{eqnarray*}

@@

	And since $B_{m} \subset E_{m}$, $b(Pu,Pu) \leq \lambda_{m}$ for all $u\in B_{m}$\\

	Using the Rayleigh quotient, and the definition of $\mu_{m}^{h}$, 
	\begin{eqnarray*}
		R(Pu) &=& \frac{b(Pu,Pu)}{(Pu,Pu)},\\
			&=& \frac{b(Pu,Pu)}{||Pu||^{2}},\\
			&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}.
	\end{eqnarray*}

	Together with Proposition \ref{Prop_2} it follows that
	\begin{eqnarray*}
		\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}.
	\end{eqnarray*}
\end{proof}

Following Lemma \ref{Lem_1}, and since $\lambda_{i}^{h} \geq \lambda_{i}$ it follows that $0 < \mu_{m}^{h} \leq 1$. It is now possible to define the error estimate as given in \cite{SF73}:
\begin{eqnarray*}
	\sigma_{m}^{h} = 1 - \mu_{m}^{h}.
\end{eqnarray*}

\newtheorem{Cor_1}{Corollary}
\begin{Cor_1}
	$0 \leq \sigma_{m}^{h} < 1$ and $\lambda_{m}^{h} - \lambda_{m} \leq \lambda_{m}^{h}\sigma_{m}^{h}$
\end{Cor_1}
\begin{proof}
	Starting with the result of Lemma \ref{Lem_1},
	\begin{eqnarray*}
		\lambda_{m}^{h} & \leq & \frac{\lambda_{m}}{\mu_{m}^{h}}\\
		\lambda_{m}^{h}\mu_{m}^{h}& \leq & \lambda_{m} \\
		-\lambda_{m}& \leq & -\lambda_{m}^{h}\mu_{m}^{h} \\
		\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h} -\lambda_{m}^{h}\mu_{m}^{h}\\
		\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h}\sigma_{m}^{h}
		\end{eqnarray*}
\end{proof}

This corollary give a error estimate for the eigenvalues. To prove the convergence of the eigenvalues, it is necessary to prove that the error estimate $\sigma_{m}^{h}$ converges to zero as $h \rightarrow 0$.\\

\newtheorem{Prop_3}[Prop_1]{Proposition} \label{Prop_3}
\begin{Prop_3}
	$\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}$
\end{Prop_3}
\begin{proof}
	Let $u \in B_{m}$. Then
	\begin{eqnarray*}
		||u - Pu||^{2} &=& ( u - Pu, u - Pu ), \\
						&=& ( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ), \\
						&=& 2( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ) - ( u, u ),\\
						&=& 2( u, u - Pu ) + ( Pu, Pu ) - ( u, u ).\\
	\end{eqnarray*}
	Rewriting gives
	\begin{eqnarray*}
		( u, u ) - ( Pu, Pu )  & = & 2( u, u - Pu ) - ||u - Pu||^{2}.
	\end{eqnarray*}

	Since $u \in B_{m}$, $||u||^{2} = 1$. So then
	\begin{eqnarray*}
		1 - ||Pu||^{2}  & = & 2( u, u - Pu ) - ||u - Pu||^{2}.
	\end{eqnarray*}

	On the right hand side, $1 - ||Pu||^{2} \leq 1 - \mu_{m}^{h} = \sigma_{m}^{h}$ for all $u \in B_{m}$. So then it must be that
	\begin{eqnarray*}
	\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}
	\end{eqnarray*}
\end{proof}

Proposition \ref{Prop_3} is a result given in \cite{SF73} without explaining how it is derived.\\

Introduce some new notation for ease of writing. For any $u \in E_{m}$, let $u^{*} = \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}$ where $u = \sum_{i=1}^{m} c_{i}u_{i}$.\\

\newtheorem{Prop_4}[Prop_1]{Proposition} \label{Prop_4}
\begin{Prop_4}
	For any $u \in E_{m}$
		\begin{eqnarray*}
		( u, u - Pu ) = b(u^{*} - Pu^{*}, u -Pu)
		\end{eqnarray*}
\end{Prop_4}
\begin{proof}
	For any $i = 1,2,...,m$,
	\begin{eqnarray*}
	\lambda_{i}( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu),\\
								&=& b(u_{i}, u-Pu) - b(u-Pu,Pu_{i}) \ \textrm{ (Rayleigh-Ritz Projection)},\\
								&=&  b(u_{i}, u-Pu) - b(Pu_{i},u-Pu),\\
								&=&  b(u_{i}-Pu_{i}, u-Pu).
	\end{eqnarray*}
	Multiplying by $c_{i}\lambda_{i}^{-1}$ and summation over i gives:
	\begin{eqnarray*}
	\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu),\\
								&=& b(\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}Pu_{i}, u-Pu),\\
										&=& b(u^{*}-Pu^{*}, u-Pu).
	\end{eqnarray*}
	Therefore $( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.
\end{proof}

\newtheorem{Lem_2}[Lem_1]{Lemma} \label{Lem_2}
\begin{Lem_2}
	$\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$
\end{Lem_2}
\begin{proof}
	From Proposition \ref{Prop_3},
	\begin{eqnarray*}
		\sigma_{m}^{h} & = & \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}, \\
					& \leq & \max\left\{ 2( u,u-Pu ) \ | \ u \in B_{m} \right\}. \\
	\end{eqnarray*}

	From Proposition \ref{Prop_4}, 
	\begin{eqnarray*}
		\sigma_{m}^{h} = \max\left\{ 2 b(u^{*}-Pu^{*}, u-Pu) \ | \ u \in B_{m} \right\}.
	\end{eqnarray*}

	Using the Schwartz inequality,
	\begin{eqnarray*}
		b(u^{*} - Pu^{*}, u -Pu) & \leq & ||u^{*} - Pu^{*}||||u -Pu||.
	\end{eqnarray*}

	Finally,
	\begin{eqnarray*}
		\sigma_{m}^{h} & \leq & \max\left\{ 2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}.
	\end{eqnarray*}
\end{proof}

\newtheorem{Prop_5}[Prop_1]{Proposition} \label{Prop_5}
\begin{Prop_5}
	For any $\epsilon > 0$, there exists a $\delta >0$ such that for $h<\delta$,
	\begin{eqnarray*}
	||u^{*} - Pu^{*}|| < \epsilon \ \textrm{ for each } u \in B_{m}\\
	||u - Pu|| < \epsilon \ \textrm{ for each } u \in B_{m}
	\end{eqnarray*}
\end{Prop_5}
\begin{proof}
	Consider a set of basis functions $\Phi \subset S^h$ such that $\phi^(k) = 0$ for each $\phi \in \Phi$.\\

	From the Rayleigh-Ritz Projection, $Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||\leq ||u-\Pi u||$, where $\Pi u$ is the interpolation of $u$ into $S^h$.\\

	From the Approximation Theorem, is follows that
	\begin{eqnarray*}
		||u - \Pi u|| \leq Ch^{k}||u^{(k)}||
	\end{eqnarray*}

	So for any $\epsilon > 0$, a $\delta$ can be found such that if $h<\delta$ then
	\begin{eqnarray*}
		||u - Pu|| \leq ||u - \Pi u|| \leq \epsilon
	\end{eqnarray*}
	A similar argument for $||u^{*} - Pu^{*}||$ proves the theorem.
\end{proof}

\newtheorem{Lem_3}[Lem_1]{Lemma} \label{Lem_3}
\begin{Lem_3}
	For any $\epsilon >0$ there exists a $\delta > 0$ such that
	\begin{eqnarray*}
	\sigma_{m}^{h} < \epsilon \ \textrm{ if } \ h < \delta
	\end{eqnarray*}
\end{Lem_3}
\begin{proof}
	For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
	\begin{eqnarray*}
	||u-Pu|| < \epsilon \ \textrm{ for each } \ u \in B_{m}
	\end{eqnarray*}
	This result, together with Lemma \ref{Lem_2} and Proposition \ref{Prop_5} gives the result.
\end{proof}

\newtheorem{Lem_4}[Lem_1]{Lemma} \label{Lem_4}
\begin{Lem_4}
	There exists a $\delta > 0$ such that for $h < \delta$
	\begin{eqnarray*}
	\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}
	\end{eqnarray*}
\end{Lem_4}
\begin{proof}
	Using Lemma \ref{Lem_3}, choose $\delta$ such that $\sigma_{m}^{h} < \frac{1}{2}$. Then by Lemma \ref{Lem_1} gives that $\lambda_{m}^{h} < 2\lambda_{m}$.\\

	So $\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
\end{proof}

The convergence of the eigenvalues are now proved.\\

\subsection{Convergence of the eigenfunctions}
The next step is to show the convergence of the eigenfunctions. First consider the following result.

\newtheorem{Lem_5}[Lem_1]{Lemma} \label{Lem_5}
\begin{Lem_5}
	\begin{eqnarray*}
		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& \lambda_{m}( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h} ) + \lambda_{m}^{h} - \lambda_{m}
		\end{eqnarray*}
\end{Lem_5}
\begin{proof}
	\begin{eqnarray*}
		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& b(u_{m},u_{m}) - 2b(u_{m},u^{h}_{m}) + b(u^{h}_{m},u^{h}_{m}) \\
										&=& \lambda_{m} ( u_{m}, u_{m} ) - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h}( u_{m}^{h},u_{m}^{h} )\\
										&=&  \lambda_{m} - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} \\
										&=& 2\lambda_{m} - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} - \lambda_{m}\\
										&=& \lambda_{m}( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) + \lambda_{m}^{h} - \lambda_{m}
		\end{eqnarray*}
\end{proof}

It has been shown that the eigenvalues converge to the exact eigenvalues as $h \rightarrow 0$. So from this result, it only remains to show that $( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$.\\

At this point, another assumption must be made. Assume that there are not eigenvalues with multiplicity more than 1. In other words, all the eigenvalues correspond only to one eigenfunction. In \cite{SF73}, the authors mention that for repeated eigenvalues, then the eigenfunctions can be chosen so that the main convergence results hold. This case is ommited in this dissertation.\\

\newtheorem{Lem_6}[Lem_1]{Lemma} \label{Lem_6}
\begin{Lem_6}
	For all m and j
	\begin{eqnarray*}
	(\lambda_{j}^{h} - \lambda_{m}) ( Pu_{m}, u_{j}^{h}) = \lambda_{m} ( u_{m}-Pu_{m},u_{j}^{h} )
	\end{eqnarray*}
\end{Lem_6}
\begin{proof}
	Since the term $\lambda_{m}( Pu,u^{h}_{j})$ appears on both sides of the equation, it is only required to show that
	\begin{eqnarray*}
		\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& \lambda_{m} ( u, u_{j}^{h} ).	
	\end{eqnarray*}
	Since both $u$ and $u_{j}^{h}$ are eigenfunctions, then
	\begin{eqnarray*}
		\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& b(Pu,u_{j}^{h})\\
		\lambda_{m} ( u, u_{j}^{h} ) &=& b(u,u_{j}^{h})
	\end{eqnarray*}

	Then equality follows from the definitions of the projection P.
\end{proof}

The set $\left\{u_{1}^{h},u_{2}^{h},...,u_{N}^{h}\right\}$ forms an orthonormal basis for $S^{h}$. The projection $Pu_{m}$ can be written as:
\begin{eqnarray}
	Pu_{m} &=& \sum_{j=1}^{N} ( P u_{m} ,u_{j}^{h}) u_{j}^{h}. \label{CV1}
\end{eqnarray}

From Lemma \ref{Lem_6}, it follows that $( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$. Therefore (\ref{CV1}) tells us that $Pu_{m}$ is close to $u_{m}^{h}$. The estimate for $Pu_{m} - u_{m}^{h}$ will follow from this result.\\

Following the convergence of the eigenvalues, $\exists \rho > 0$ and $\exists \delta > 0$ such that if $h<\delta$,
\begin{eqnarray}
|\lambda_{m} - \lambda_{j}^{h}| &>& \rho \ \ \textrm{ for all } \ j = 1,2,...,N.
\end{eqnarray}
Therefore
\begin{eqnarray}
\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|} &\leq & \rho \ \ \textrm{ for all } \ j = 1,2,...,N.
\end{eqnarray}

\newtheorem{Lem_7}[Lem_1]{Lemma} \label{Lem_7}
\begin{Lem_7}
	\begin{eqnarray*}
		||Pu - QPu||^{2} &\leq & {\rho}^{2} ||u_{m} - Pu_{m}||^{2}
	\end{eqnarray*}
\end{Lem_7}
\begin{proof}

Using Lemma \ref{Lem_6}:
\begin{eqnarray*}
||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2},\\
				&\leq & \rho^{2} \sum_{j\neq m} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
				&\leq & \rho^{2} \sum_{j=1}^{N} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
				& = & \rho^{2} ||u - Pu||^{2}.\\
\end{eqnarray*}
\end{proof}

\newtheorem{Lem_8}[Lem_1]{Lemma} \label{Lem_8}
\begin{Lem_8}
	\begin{eqnarray*}
		||u_{m} - \beta u_{m}^{h}|| &\leq & \left(1+\rho\right)||u_{m}-Pu_{m}||
	\end{eqnarray*}
\end{Lem_8}
\begin{proof}
	\begin{eqnarray*}
	||u_{m} - \beta u_{m}^{h}|| & \leq & ||u_{m}-Pu_{m}|| + ||Pu_{m} - \beta u_{m}^{h}|| \\
				& \leq & \left(1+\rho\right)||u_{m}-Pu_{m}|| \ \ \textrm{ (by Lemma \ref{Lem_7})}
	\end{eqnarray*}
\end{proof}
